Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-03-21 fully-abstract-comp/technical-report.tex
spelling

%%% Named registers
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\rstk}{\mathrm{r}_\mathrm{stk}}
\newcommand{\rO}{\mathrm{r}_0}

@@

\subsection{Compiler}
\[
\comp{\cdot} : \src{i}^* \fun \trg{i}^*
\]
\clearpage
\section{Examples}
\subsection{Capabilitiy opacity}
The following pseudo program demonstrates the need of opaque capabilities. If we assume a system with no opaque capabilities, then the following programs break compiler corretness
\begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
p1 ::= if r1 is length 2 then
         call r1 with the following callback in r5:
           {put $\textit{\texttt{diverging}}$ closure in r2;
            return};
         halt
       else diverge

>>>>

%%% Named registers
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\rstk}{\mathrm{r}_\mathrm{stk}}
\newcommand{\rO}{\mathrm{r}_\mathrm{ret}}

@@

\subsection{Compiler}
\[
\comp{\cdot} : \src{i}^* \fun \trg{i}^*
\]
\clearpage
\section{Examples}
\subsection{Capability opacity}
The following pseudo program demonstrates the need of opaque capabilities. If we assume a system with no opaque capabilities, then the following programs break compiler correctness
\begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
p1 ::= if r1 is length 2 then
         call r1 with the following callback in r5:
           {put $\textit{\texttt{diverging}}$ closure in r2;
            return};
         halt
       else diverge
